Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-05-23 ms.tex
More descriptive section title
Oops, missed lowercase signal variable

\section{Setup}

@@

In the frequency domain, the strain $X (\omega)$ observed by a detector is a linear combination of two orthogonal \ac{GW} quadratures and additive noise,
%
\begin{equation}\label{eq:signal-model}
	x (\omega) = h (\omega, \rho, \gamma, \tau) + n (\omega) = \frac{\rho}{\sigma} e^{i (\gamma - \omega \tau)} u (\omega) + n (\omega),
\end{equation}
%
where $h (\omega)$ is the signal content, $n (\omega)$ is the detector's \ac{WSS} Gaussian noise with \ac{PSD} $S(\omega)$, $u (\omega)$ is the frequency-domain post-Newtonian inspiral signal, $\rho$ is the signal's amplitude, $\gamma$ is a phase angle the encodes the relative strength of two \ac{GW} quadratures, and $\tau$ is the time of arrival relative to an arbitrary time base. The quantity $\sigma$ is a normalization constant defined as the \ac{SNR} of the \ac{GW} source at a fiducial distance, here taken to be $D_\mathrm{fiducial} = 1$~Mpc,
%
\begin{equation}\label{eq:sigma}
    \sigma^2 = \int_0^\infty \frac{\left| u (\omega)\right|^2}{S(\omega)} \, \mathrm{d}\omega.
\end{equation}
%
The distance at which an optimally oriented \ac{GW} source would produce \ac{SNR}=1 is defined as $D_1 = D_\mathrm{fiducial} / \sigma$. The likelihood, or the probability of obtaining the observation $x(\omega)$ conditioned on the value of the parameter vector $\boldsymbol\theta = (\rho, \gamma, \tau)$, is Gaussian, with the log-likelihood proportional to:
%
\begin{equation}\label{eq:gaussian-likelihood}
	\mathcal{L}(x; \boldsymbol\theta) = p(x | \boldsymbol\theta)
		\propto \exp \left[
		- \frac{1}{2} \int_0^\infty \frac{\left|x (\omega)
			- h(\omega; \boldsymbol\theta) \right|^2}{S(\omega)} \, \mathrm{d}\omega
	\right].
\end{equation}

>>>>

\section{Theory of \ac{GW} detection and parameter estimation}

@@

In the frequency domain, the strain $x (\omega)$ observed by a detector is a linear combination of two orthogonal \ac{GW} quadratures and additive noise,
%
\begin{equation}\label{eq:signal-model}
	x (\omega) = h (\omega, \rho, \gamma, \tau) + n (\omega) = \frac{\rho}{\sigma} e^{i (\gamma - \omega \tau)} u (\omega) + n (\omega),
\end{equation}
%
where $h (\omega)$ is the signal content, $n (\omega)$ is the detector's \ac{WSS} Gaussian noise with \ac{PSD} $S(\omega)$, $u (\omega)$ is the frequency-domain post-Newtonian inspiral signal, $\rho$ is the signal's amplitude, $\gamma$ is a phase angle the encodes the relative strength of two \ac{GW} quadratures, and $\tau$ is the time of arrival relative to an arbitrary time base. The quantity $\sigma$ is a normalization constant defined as the \ac{SNR} of the \ac{GW} source at a fiducial distance, here taken to be $D_\mathrm{fiducial} = 1$~Mpc,
%
\begin{equation}\label{eq:sigma}
    \sigma^2 = \int_0^\infty \frac{\left| u (\omega)\right|^2}{S(\omega)} \, \mathrm{d}\omega.
\end{equation}
%
The distance at which an optimally oriented \ac{GW} source would produce \ac{SNR}=1 is defined as $D_1 = D_\mathrm{fiducial} / \sigma$. The likelihood, or the probability of obtaining the observation $x(\omega)$ conditioned on the value of the parameter vector $\boldsymbol\theta = (\rho, \gamma, \tau)$, is Gaussian, with the log-likelihood proportional to:
%
\begin{equation}\label{eq:gaussian-likelihood}
	\mathcal{L}(x; \boldsymbol\theta) = p(x | \boldsymbol\theta)
		\propto \exp \left[
		- \frac{1}{2} \int_0^\infty \frac{\left|x (\omega)
			- h(\omega; \boldsymbol\theta) \right|^2}{S(\omega)} \, \mathrm{d}\omega
	\right].
\end{equation}
